Watch Out for the Bully! Study of Interference Between Jobs Running Concurrently on Dragonfly Network

### 2016-03-08 draft.tex
add section job placement and routing

\section{Job Placement and Routing}
\label{sec:placement-routing}

@@

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{syn-wkld/amg10/lc-traffic}
        \caption{AMG Local Channel Traffic}
        \label{fig:samg-lc-traffic}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{syn-wkld/mg/lc-traffic}
        \caption{MG Local Channel Traffic}
        \label{fig:syn-mg-lc-traffic}
    \end{subfigure}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{syn-wkld/cr/lc-traffic}
        \caption{CR Local Channel Traffic}
        \label{fig:syn-cr-lc-traffic}
    \end{subfigure}%
   \caption{Each Application Router Local Channel Traffic.  }
   \label{fig:syn-3app-lc-traffic}
\end{figure*}

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{syn-wkld/amg10/gc-traffic}
        \caption{AMG Global Channel Traffic}
        \label{fig:samg-gc-traffic}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{syn-wkld/mg/gc-traffic}
        \caption{MG Global Channel Traffic}
        \label{fig:syn-mg-gc-traffic}
    \end{subfigure}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{syn-wkld/cr/gc-traffic}
        \caption{CR Global Channel Traffic}
        \label{fig:syn-cr-gc-traffic}
    \end{subfigure}%
   \caption{Each Application Router Global Channel Traffic.}
   \label{fig:syn-3app-gc-traffic}
\end{figure*}

@@

\section{Better Orchestration }
According to our findings, we believe choosing the ideal placement and routing strategies for workload running on dragonfly network should be based on application's communication intensity. The less intensive applications should avoid sharing network resource with other applications, reduce the possible interference. Contiguous placement and adaptive routing can guarantee the QoS for the less intensive applications.

The communication-intensive applications tend to cause local congestion. Random placement and adaptive routing can ...

>>>>

\subsection{Network Configuration}
\label{sec: network config}

 Here will talk about network configuration, such as network scale, link bandwidth etc. \\

\subsection{Job Placement}
\label{sec:placement-routing}

Job placement refers to the scheme used by batch scheduler to allocate the required number of nodes by the job for execution. There are many works study various ways of doing job placement on HPC systems with different topologies \cite{yang-cluster14} \cite{zhou-ipdps15} \cite{hoefler-hpdc14}. In this work, we study the following two placement schemes:

\textbf{Contiguous Placement:} In this scheme, the nodes will first be indexed consecutively in the increasing oder of their group id and router id. The job is allocated by cutting chunks of nodes from the sequentially ordered list. The nodes been allocated to each job will be adjacent to each other, usually they are attached to the same router, in the same group. Contiguous placement confines the traffic of application into the local area, which may leads to local network congestion and increase the possibility of hot-spots.

\textbf{Random Placement:} In this scheme, job will get a set of nodes that randomly selected from all the available nodes in the system. The nodes allocated to each job would be attached to different routers in different groups. Some routers may be shared by different applications when using random placement. Random placement can spreading the traffic of application uniformly across the whole system, thus avoid the possible hot-spots and reach load balance.

\subsection{Routing Schemes}
\label{sec:routing}

The implemented routing schemes in CODES dragonfly network model are based on the routing algorithm proposed by Kim et al. \cite{dally-dragonfly}. Two routing schemes studied in this work are \emph{Minimal} and \emph{Adaptive}.

\textbf{Minimal:} The minimal routing sends a message from source router to destination router along the shortest path. When there are multiple shortest paths, the message is evenly divided among the paths. Minimal routing can guarantee the minimum hops the message takes from source to destination. However, it may leads to congestion along the shortest path.

\textbf{Adaptive:} In this scheme, the path a message takes will be adaptively chosen between shortest and non-shortest path, depends on the congestion situation along that path. For the non-shortest path, an intermediate router will be randomly chosen. The message will first take the shortest path from source to that intermediate router, then it will take the shortest path between the intermediate router to the destination. Since adaptive scheme chooses routing path adaptively based on the congestion situation, it can void local congestion and reduce the possibility of hot-spots.

@@

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/amg10/lc-traffic}
        \caption{AMG Local Channel Traffic}
        \label{fig:samg-lc-traffic}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/mg/lc-traffic}
        \caption{MG Local Channel Traffic}
        \label{fig:syn-mg-lc-traffic}
    \end{subfigure}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/cr/lc-traffic}
        \caption{CR Local Channel Traffic}
        \label{fig:syn-cr-lc-traffic}
    \end{subfigure}%
   \caption{Each Application Router Local Channel Traffic.  }
   \label{fig:syn-3app-lc-traffic}
\end{figure*}

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/amg10/gc-traffic}
        \caption{AMG Global Channel Traffic}
        \label{fig:samg-gc-traffic}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/mg/gc-traffic}
        \caption{MG Global Channel Traffic}
        \label{fig:syn-mg-gc-traffic}
    \end{subfigure}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/cr/gc-traffic}
        \caption{CR Global Channel Traffic}
        \label{fig:syn-cr-gc-traffic}
    \end{subfigure}%
   \caption{Each Application Router Global Channel Traffic.}
   \label{fig:syn-3app-gc-traffic}
\end{figure*}

@@

According to our findings, we believe choosing the ideal placement and routing strategies for workload running on dragonfly network should be based on application's communication intensity. The less intensive applications should avoid sharing network resource with other applications, reduce the possible interference. Contiguous placement and adaptive routing can guarantee the QoS for the less intensive applications, thus prevent the ``bully" from happening.

The communication-intensive applications tend to cause local congestion. It is preferable to enable communication-intensive applications to have extra network resource by sharing with other applications.  Random placement and adaptive routing can alleviate the local congestion by redirecting traffic to other less busy routers in the network.

So the ideal placement and routing strategies for workload running on dragonfly network should be like this. The communication-intensive applications should be randomly allocated over the system and adaptive routing should be used by these applications to alleviate the local congestion. On the other hand, less intensive application should get contiguous allocation, minimal routing should be used by these applications to avoid network sharing and reduce interference.
